---
title: "Devlog 0.0.0.9002 Full Database & Create Object"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{devlog_0_0_0_9002_full_database_and_create_object}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ttnotion)
```

## Setup token and database id
```{r eval=FALSE, include=FALSE}
token_setup_global()
id_setup_global("d6e04cf5f53e484d9e54b9618a32e5be")
```

## Query database
```{r eval=FALSE, include=FALSE}
database_list <- ttnotion::database_query()
```

Bug: cursor not work while more than 200 records[done]

Note: wait without message[todo]

## Plan

1. query more than 100 [done]

2. detect column type

  Name "title"
  大类 "multi_select"
  类别 "multi_select"
  时间 "date"
  详情 "rich_text"
  日期 "date"
  地点 "rich_text"
  
  title[done]
    Name
  multi_select
    大类
    类别
  date[done]
    时间
    日期
  rich_text
    详情
    地点

3. create object and method

## Create Object

### notion_title
```{r eval=FALSE, include=FALSE}
title_1 <- object_create_title(database_list$results[[1]]$properties$Name)
```

debug: NULL caused new object element length bug

### notion_multi_select
```{r eval=FALSE, include=FALSE}
multi_select_1 <- object_create_multi_select(database_list$results[[17]]$properties$类别)
multi_select_1
```

### notion_date
```{r eval=FALSE, include=FALSE}
date_1 <- object_create_date(database_list$results[[17]]$properties$时间)
## show
date_1
## is
is.notion_date(date_1)
## filter
notion_filter(date_1,min="2022-05-22",max="2022-05-28")
notion_filter(date_1,min="2022-05-20",max="2022-05-22")
```

### notion_rich_text

same with title

```{r eval=FALSE, include=FALSE}
input <- database_list$results[[1]]$properties$详情
input_null <- database_list$results[[1]]$properties$地点

rich_text_1 <- object_create_rich_text(input)
rich_text_2 <- object_create_rich_text(input_null)
```

